\chapter{Changelog}
\hypertarget{md_node__modules_2zod-to-json-schema_2changelog}{}\label{md_node__modules_2zod-to-json-schema_2changelog}\index{Changelog@{Changelog}}
\label{md_node__modules_2zod-to-json-schema_2changelog_autotoc_md36320}%
\Hypertarget{md_node__modules_2zod-to-json-schema_2changelog_autotoc_md36320}%


\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{2}{|X[-1]}|}
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Version   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Change    }\\\cline{1-2}
\endfirsthead
\hline
\endfoot
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Version   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Change    }\\\cline{1-2}
\endhead
3.\+24.\+5   &Update .npmignore to drop 2 mb of test files. Thanks \href{https://github.com/mmkal}{\texttt{ Misha Kaletsky}}!    \\\cline{1-2}
3.\+24.\+4   &Added options to set the value of additional\+Properties in objects and record    \\\cline{1-2}
3.\+24.\+3   &Adds post\+Process callback option    \\\cline{1-2}
3.\+24.\+2   &Restructured internals to remove circular dependencies which apparently might cause some build systems to whine a bit. Big thanks to \href{https://github.com/NanezX}{\texttt{ Víctor Hernández}} for the fix.    \\\cline{1-2}
3.\+24.\+1   &Adds Open\+AI target    \\\cline{1-2}
3.\+24.\+0   &Implements new string checks (jwt, base64url, cidr ipv4/v6), matching the new Zod version    \\\cline{1-2}
3.\+23.\+5   &Module import hotfix by \href{https://github.com/enzomonjardin}{\texttt{ Enzo Monjardín}}. Thanks!    \\\cline{1-2}
3.\+23.\+4   &Fixes branded regex property names and a weird edgecase in arrays. Thanks to \href{https://github.com/imsanchez}{\texttt{ Isaiah Marc Sanchez}} and \href{https://github.com/mitchell-merry}{\texttt{ Mitchell Merry}}!    \\\cline{1-2}
3.\+23.\+3   &More tests (Thanks \href{https://github.com/brettz9}{\texttt{ Brett Zamir!}}), removed dead code    \\\cline{1-2}
3.\+23.\+2   &Lazily loads Emoji regex to avoid incompatibility with some environments. Thanks \href{https://github.com/jacoblee93}{\texttt{ Jacob Lee}}!    \\\cline{1-2}
3.\+23.\+1   &Best-\/effort Reg\+Ex flag support by \href{https://github.com/Spappz}{\texttt{ Spappz}}! Some minor fixes and additions, such as the title option.    \\\cline{1-2}
3.\+23.\+0   &Adds support for base64, date, time, duration and nanoid string validations. A warm welcome and a big thanks to \href{https://www.github.com/colinhacks}{\texttt{ Colin}}, the creator of Zod, joining in as a contributor \+:)    \\\cline{1-2}
3.\+22.\+5   &Adds new z.\+date() parsing options and override callback    \\\cline{1-2}
3.\+22.\+4   &Adds fix for nullable references in Open\+API mode    \\\cline{1-2}
3.\+22.\+3   &Adjust root path from "{}\#/"{} to "{}\#"{} according to RFC 6901    \\\cline{1-2}
3.\+22.\+2   &Adds "{}output"{} pipe strategy    \\\cline{1-2}
3.\+22.\+1   &Fixes broken imports when using some bundlers    \\\cline{1-2}
3.\+22.\+0   &Support readonly. Export both CJS and ESM. Export everything from index. Alternative map parser. Improved pattern handling and updated sources.    \\\cline{1-2}
3.\+21.\+4   &Fixes missing support for exact array length    \\\cline{1-2}
3.\+21.\+3   &Fixes issue \#77 (Reference path to nullable schemas in Open-\/\+API mode)    \\\cline{1-2}
3.\+21.\+2   &Adds "{}integer"{} type Date output to support min/max checks, markdown\+Description option, fixes "{}none"{} ref\+Strategy by adding "{}seen"{} and adds an option to use "{}pattern"{} with Zods\textquotesingle{} email enum instead of "{}format"{}.    \\\cline{1-2}
3.\+21.\+1   &New target (2019-\/09) along with improved intersection schemas, improved mutual recursion references in definitions, descriptions respected in union parser and not removed in collapsed    \\\cline{1-2}
3.\+21.\+0   &Added new string validations (ip, emoji, etc) and Big\+Int checks to support Zod 3.\+21    \\\cline{1-2}
3.\+20.\+5   &Added unique\+Items to Set and an option to disregard pipe schemas    \\\cline{1-2}
3.\+20.\+4   &Bugfixes and improved record parsing for open\+Api3    \\\cline{1-2}
3.\+20.\+3   &Added Cuid2 support introduced in Zod 3.\+20.\+3    \\\cline{1-2}
3.\+20.\+2   &Reintroduced conditional simplified return-\/type for when target is Open\+API 3    \\\cline{1-2}
3.\+20.\+1   &Fixed inconsistent casing in imports    \\\cline{1-2}
3.\+20.\+0   &Adds support for Zod 3.\+20 with catch and pipe parser as well as new string validations. Refactored Ref handling; adding definitions no longer considered experimental. Main API function refactored and simplified; output type less defined but a lot easier to maintain. Doubt anyone will miss it. ~\newline
$<$quote$>${\itshape Narrator\+: Someone did in fact miss it}$<$/quote$>$    \\\cline{1-2}
3.\+19.\+4   &Adds custom error message support    \\\cline{1-2}
3.\+19.\+3   &Mark {\ttfamily definitions} as experimental in the readme    \\\cline{1-2}
3.\+19.\+2   &Added {\ttfamily definitions} option    \\\cline{1-2}
3.\+19.\+1   &Strict unions fix    \\\cline{1-2}
3.\+19.\+0   &No new features added in Zod, parity bump    \\\cline{1-2}
3.\+18.\+2   &Fixes support for native enums    \\\cline{1-2}
3.\+18.\+1   &Add strict\+Unions options    \\\cline{1-2}
3.\+18.\+0   &Added support for branded types    \\\cline{1-2}
3.\+17.\+2   &Fix for reference paths when supplying name option string.    \\\cline{1-2}
3.\+17.\+1   &Added starts\+With and ends\+With string checks. Merge multiple pattern checks into all\+Of array.    \\\cline{1-2}
3.\+17.\+0   &Added switch case handler for new trim "{}check"{}. No changes to functionality.    \\\cline{1-2}
3.\+15.\+x -\/ 3.\+16.\+x   &Skipped\+: Did not change the Zod API in any way relevant for this package.    \\\cline{1-2}
3.\+14.\+1   &Dependabot security updates    \\\cline{1-2}
3.\+14.\+0   &Moves Zod into peer\+Dependencies. Supports checks for sets, Na\+N-\/type (sort of), discriminated union type and standalone optional properties (as unions with undefined)    \\\cline{1-2}
3.\+12.\+x -\/ 3.\+13.\+x   &Skipped    \\\cline{1-2}
3.\+11.\+3   &Joins unions of enums into single enum and allows enums as keys of records    \\\cline{1-2}
3.\+11.\+2   &Adds option to target Open API 3 spec (paths) instead of Json Schema 7.    \\\cline{1-2}
3.\+11.\+1   &Performance boost when using \$ref\+Strategy {\ttfamily none} and internal improvements.    \\\cline{1-2}
3.\+11.\+0   &Added description support introduced in Zod 3.\+11.\+5    \\\cline{1-2}
3.\+10.\+x   &Skipped\+: Minor 10 did not change the Zod API    \\\cline{1-2}
3.\+9.\+5   &Type bug fix\+: used dev dependency types in package    \\\cline{1-2}
3.\+9.\+4   &Path bug fix and test case when using optional definitions path    \\\cline{1-2}
3.\+9.\+3   &Added option to change definition property name to \$defs    \\\cline{1-2}
3.\+9.\+2   &Added option to handle transform results as any instead of relying on their input schema.    \\\cline{1-2}
3.\+9.\+1   &Refactored the way reference pointers are passed around and added options pattern to main function without braking backwards compatibility! You can now add a base path, change the reference strategy (or opt out), and still set the schema name inside the options object or outside as before.    \\\cline{1-2}
3.\+9.\+0   &Added support for multiple\+Of number validaion, .rest() schemas for tuples and key validation for records (only compatible with string keys due to JSON Schema limitation).    \\\cline{1-2}
3.\+7.\+x -\/ 3.\+8.\+x   &Skipped to reach functional parity with Zod versioning.    \\\cline{1-2}
3.\+6.\+1   &Realised intersection had another potential ref pathing bug. Fixed.    \\\cline{1-2}
3.\+6.\+0   &Added support for default \& effects (refine). Broke out changelog.\+md    \\\cline{1-2}
3.\+5.\+0   &Added support for CUID string validation    \\\cline{1-2}
3.\+4.\+3   &Fixed \$ref pathing for catchall and intersection. Additional tests and code structure fixes.    \\\cline{1-2}
3.\+4.\+2   &Fixed broken intersection parser (Thanks \href{https://github.com/Noah2610}{\texttt{ Noah2610}}!)    \\\cline{1-2}
3.\+4.\+1   &Fixed pathing bug for nullable items.    \\\cline{1-2}
3.\+4.\+0   &Added support for z.\+lazy()    \\\cline{1-2}
3.\+3.\+0   &Added support for catchall (additional\+Properties schema on objects). Rebuilt object parser.    \\\cline{1-2}
3.\+2.\+0   &Added support for Map and Set as seen by their most common JSON definitions. Beware no standardized definition seem to exist and JSON.\+parse doesn\textquotesingle{}t handle either natively. Their implementations here are based on the spread approach. Also further simplified intersection definition to just all\+Of.    \\\cline{1-2}
3.\+1.\+0   &String patterns finally supported! Fixed bugs include broken external type, unsafe nullable parsing, bad intersection implementation, and missing support for passthrough keys in objects.    \\\cline{1-2}
3.\+0.\+3   &Fixed array deep pathing bug (path contained {\ttfamily array} instead of {\ttfamily items})    \\\cline{1-2}
3.\+0.\+2   &Fixed broken type usage (Non\+Empty\+Array\+Definition was removed from Zod)    \\\cline{1-2}
3.\+0.\+1   &Fixed a typo in the readme    \\\cline{1-2}
3.\+0.\+0   &Compatible with Zod 3.\+2.\+0. Huge props to \href{https://github.com/mrhammadasif}{\texttt{ Mr Hammad Asif}} for his work on this.    \\\cline{1-2}
0.\+6.\+2   &Hotfix for undefined object properties. Could crash the parser when using Pick    \\\cline{1-2}
0.\+6.\+1   &Fixed bug in union pathing. {\ttfamily \$Ref} was missing {\ttfamily /any\+Of}    \\\cline{1-2}
0.\+6.\+0   &Moved {\ttfamily @types/json-\/schema} and {\ttfamily typescript} to dev dependencies. {\ttfamily @types/json-\/schema} is now only used for the test suites. Using {\ttfamily strict\+: true} in ts config.    \\\cline{1-2}
0.\+5.\+1   &First working release with all relevant Zod types present with most validations (except for string patterns due to Zod not exposing the source regexp pattern for those).    \\\cline{1-2}
\texorpdfstring{$<$}{<} 0.\+5.\+1   &Deprecated due to broken package structure. Please be patient, I eat crayons.   \\\cline{1-2}
\end{longtabu}
